Supplementary Information

### 2021-04-30 markdown/si.Rmd
fix typo

In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level. The MAE is commonly used to measure how different an estimated set of numbers are from their real value. Because it seems possible that these errors could be larger in smaller municipalities, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.

>>>>

In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level. The MAE is commonly used to measure how different an estimated set of numbers are from their real value. Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.

### 2021-04-30 markdown/si.tex
fix typo

In Table \ref{tab:mae} we present the mean average error (MAE) of the L2 estimates aggregated up to the municipality level. The MAE is commonly used to measure how different an estimated number is from its real value. Because it seems possible that these errors could be larger in smaller municipalities, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.

>>>>

In Table \ref{tab:mae} we present the mean absolute error (MAE) of the L2 estimates aggregated up to the municipality level. The MAE is commonly used to measure how different an estimated set of numbers are from their real value. Because it seems possible that these errors vary by population size, we present the MAE for each quartile of the set of municipalities as measured by population, as well as the overall MAE.
